### 2024-06-08 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

### Figure 2
### --------------------------------------------------------------------------------------------------------------------------------------------

>>>>

```{r Fig S1j}

load(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\argBC.RData)')
load(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\bacBC.RData)')
load(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\pwyBC.RData)')
argBC$Microbiome = 'ARG'
bacBC$Microbiome = 'Bacteria'
pwyBC$Microbiome = 'Pathway'
allBC = rbind(argBC, pwyBC,bacBC)
allBC$Group %<>% factor(., levels = c('Within hospital', 'Between hospital'))
allBC$Microbiome %<>% factor(., levels = c('Bacteria', 'Pathway', 'ARG'))
table(allBC$Microbiome )
bc = ggplot(allBC, aes(x = Group, y = value, fill = Group)) +
  geom_boxplot(outlier.size = 0.5) +
  stat_compare_means(hjust = -1,label = 'p.signif') +
  scale_y_continuous(expand = expansion(add = c(0.02, 0.1))) +
  scale_fill_manual(values = c('#DEDEDE', '#9AD7C6')) +
  facet_wrap(.~Microbiome) +
  labs(y = 'Bray-Curtis dissimilarity') +
  mytheme3 + theme(strip.text = element_text(size = 13), axis.text.x = element_blank(),
                   legend.position = 'top', legend.direction = 'horizontal')
pdf('./bc_boxplot.pdf', width = 4.68, height = 3.33)
print(bc)
dev.off()

```
### Figure 2
### --------------------------------------------------------------------------------------------------------------------------------------------
